---
title: "README"
author: "Stephane"
date: "10/02/2021"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r read}
knitr::read_chunk("exemple.R")
```

```{r mock individual data}

```
## Generate reports by region
- First, we create a mock dataset with 
    - `r k` *régions*
    - For each *région* a variable number of *départements*
    - For each *département*, up to `r netab` types of *établissements* (`typ_etab`), also variable
    - And two numeric variables (with missing values) to be summarized by `typ_etab`
- It looks like this :

```{r}
knitr::kable( rbind(head(df0), tail(df0)) )
```

- We want to summarize values by `typ_etab` and this is done with a simple function

```{r summarize function, echo = TRUE}

```

- Now we can look at global results
```{r table France}

```

```{r}
knitr::kable( tabfr )
```

- Then, for each *région*, we apply `ftab` for the whole region and for each *département* within this region. All tables are saved in a named list.

```{r table regions}

```

```{r, echo = TRUE}
str(ltab)
```


- Finally, elements of the list can be parsed to `exemple_rapport.Rmd` to generate a report, individually or for all regions in the list.
```{r unit report}

```

- To generate one report which is saved with time stamp
```{r, echo = TRUE, eval = FALSE}
 unit_report(reg = "A")
```

- To generate all reports
```{r all reports, echo = TRUE, eval = FALSE}

```




